Tor's Usability for Censorship Circumvention

### 2015-04-16 PETS2015-paper/paper.tex
Put equals sign inside $$.
Slightly better formatting for resources.

We recruited five journalists from Berkeley by reaching out to journalist contacts. 
%Demographics here. 
During the study, we recorded their screen, what they were saying out loud in their cognitive walk through, and also cast their screen into a room with Tor developers. The participants also took an exit survey which estimated their familiarity with technology and security. On average, participants took 26 minutes to complete the study ($\sigma$ = 7 min).  The result was that people did have difficulty with downloading the Tor browser because of the gatekeeper icon, did not understand what many of the many options meant, and were confused about why certain things were happening.

@@

These are online artifacts of our completed pilot study.

\noindent \url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}\\
\noindent \url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}\\
\indent Summary and results of the study.

\noindent \url{https://people.torproject.org/~dcf/uxsprint2015/}\\
\indent Subtitled screen recordings.

>>>>

We recruited five journalists from Berkeley by reaching out to journalist contacts. 
%Demographics here. 
During the study, we recorded their screen, what they were saying out loud in their cognitive walk through, and also cast their screen into a room with Tor developers. The participants also took an exit survey which estimated their familiarity with technology and security. On average, participants took 26 minutes to complete the study ($\sigma = 7$~min).  The result was that people did have difficulty with downloading the Tor browser because of the gatekeeper icon, did not understand what many of the many options meant, and were confused about why certain things were happening.

@@

These are online artifacts of our completed pilot study.
Summary and results, including resulting browser changes:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}
\item \url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}
\end{itemize}

Subtitled screen videos:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://people.torproject.org/~dcf/uxsprint2015/}
\end{itemize}
